Adaptive mesh refinement provides a robust and efficient approach to investigate effects of mesh resolution on the numerical solution.
A common approach to drive adaptive mesh refinement is through the use of an error estimator.
The basic principle behind this approach is that discretization error should be ideally equidistributed \cite{baker1997mesh}, since the accuracy of the simulation is bounded by the worst-resolved features.
For complex fluid flow problems, it is not known \textit{a priori} where important flow features will occur. Thus, it is desirable to adapt the mesh based on an a posteriori error estimator.

A wide range of error estimators, both explicit and implicit, have been developed and studied in the literature in the past few decades.
%For a comprehensive review see Ainsworth ~\cite{ainsworth2011book}.
Some of the early work by Babuska and Rheinboldt~\cite{babuvska1978posteriori} focused on the inter-element jump terms to derive an explicit error estimate.
Zienkiewicz and Zhu~\cite{zienkiewicz1992superconvergent1,zienkiewicz1992superconvergent2} introduced a superconvergent patch recovery, a method that motivated an explicit error estimate based on recovered gradients (commonly referred to as the ZZ-error estimator).
Ainsworth and Oden~\cite{ainsworth2011book}, and Verf\"urth~\cite{verfurth1994posteriori} provide a detailed review of more error estimators for elliptic problems.
For implicit methods, Bank and Weiser \cite{bank1985some} proposed an approach for solving local Neumann problems to obtain an error estimate for elliptic problems.
This approach was further extended by Oden, Wu, and Ainsworth \cite{oden1994posteriori} for steady incompressible Navier-Stokes equations, which was referred to as the element residual method.
A further extension for this implicit method to the unsteady incompressible Navier-Stokes formulation was provided by Prudhomme and Oden~\cite{prudhomme1999posteriori}.
An improvement upon the element residual method is the equilibrated residual method that imposes additional constraints upon the Neumann problem which Ainsworth et al.\cite{ainsworth2013fully} applies to advection-diffusion-reaction systems in multidimensions.
Explicit error estimators are inherently cheaper than implicit error estimators because an additional problem does not need to be solved, thus making it attractive for large-scale applications.

More recently, the variational multiscale (VMS) framework has been used to develop explicit error estimators. 
The VMS framework, proposed by Hughes and co-workers ~\cite{hughes1995multiscale,hughes1998variational}, splits the solution into a coarse-scale solution and a fine-scale solution. 
The coarse-scale solution is obtained numerically while the fine-scale solution is modeled. 
A number of approaches have been proposed to model the fine-scale solution, for example, see \cite{brezzi1997b,brezzi1992relationship,brezzi1994choosing,codina2002stabilized,hughes2007variational,principe2010stabilization}. 
The fine-scale Green's function is also used to formulate an \textit{a posteriori} error estimate by Hauke and co-workers \cite{hauke2006proper,hauke2006multiscale,hauke2008variational,hauke2012mesh,hauke2014recent,hauke2015variational,irisarri2016posteriori} and others \cite{bayona2018variational}.
In this work, we employ the VMS-based error estimator
since the VMS framework is currently used for LES and it is computationally inexpensive

Error estimators and correction indicators have been used in a wide range of problems to drive mesh adaptation. These include both isotropic and anisotropic mesh adaptation and for both steady and unsteady problems. For flow problems, mesh adaptation has been shown to provide significant computational savings or better accuracy for a variety of problems. For example, for boundary layer flows \cite{bib:Sahni2008,bib:Sahni2017_adapt} including turbulent flows \cite{bib:Chitale2015}. Similarly, mesh adaptation has been applied for unsteady cardiovascular flows \cite{bib:Muller2005,bib:Sahni2006,bib:Sahni2009} including high-order meshes \cite{bib:Sahni2010}. In particular, cardiovascular flows are typically periodic in time (i.e., based on the cardiac cycle) and in this scenario one can construct an adapted mesh that would be appropriate for the entire cardiac cycle. This can be done by applying error estimation or correction indication at several pre-defined instants of the cycle and then combine them into a single one that meets the requirements for the entire cycle. A similar strategy is used in this work. On the other hand, for a fully unsteady problem (without any periodic behavior), mesh adaptation can be applied repeatedly over time, which is relatively more expensive. For example, unsteady mesh adaptation has been applied to unsteady problems with two-phase flows \cite{bib:rodriguez2013} and evolving shocks and geometry \cite{bib:Yang2021}.


% A parallel interface tracking approach for evolving geometry problems \cite{bib:Yang2021}.

%Parallel anisotropic mesh adaptation with boundary layers for automated viscous flow simulations \cite{bib:Sahni2017_adapt}.

%Anisotropic Adaptation for Transonic Flows with Turbulent Boundary Layers \cite{bib:Chitale2015}

%A parallel adaptive mesh method for the numerical simulation of multiphase flows \cite{bib:rodriguez2013}

% Curved boundary layer meshing for adaptive viscous flow simulations \cite{bib:Sahni2010}

%Automated adaptive cardiovascular flow simulations \cite{bib:Sahni2009}

%Adaptive boundary layer meshing for viscous flow simulations \cite{bib:Sahni2008}

%Efficient anisotropic adaptive discretization of the cardiovascular system \cite{bib:Sahni2006}

%Anisotropic adaptive finite element method for modelling blood flow \cite{bib:Muller2005}

