%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
%                                                                 %
%                         ACKNOWLEDGEMENT                         %
%                                                                 %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
 
\specialhead{ACKNOWLEDGMENT}
 
First and foremost, I would like to thank my advisor, Prof. Onkar Sahni. 
Without his continued guidance and mentorship, this work would not have been possible.
Through the difficulties and challenges that have accompanied this doctoral journey, he has been a constant source of support and leadership that I have looked up to.

I would also like to thank my committee members, Prof. Mark Shephard, Prof. Farhan Gandhi, and Prof. Christopher Letchford, who have provided technical insights and contributions for this work.

I would like to acknowledge the computational resources that were used in this work, namely the Scientific Computation Research Center (SCOREC) and Center for Computational Innovations (CCI).
SCOREC has been a truly supportive and collaborative environment, and I have had the pleasure and privilege of working closely with brilliant colleagues over the past few years.
I would like to thank Alex Kocher, who, during my first semester, showed me the ropes to the tools I ended up using throughout my doctoral pursuit.
Also special thanks to Vignesh Srinivasaragavan who helped me implement and test the error-estimator used in this work.
My deepest gratitudes to Dr. Alvin Zhang and Dr. Kinshuk Panda, who were a constant source of support and friendship both inside and outside of lab; to Dr. Zelu Xu, who I could talk to about anything; and to Dr. Jason Li, who helped me foster my Paraview skills.
I would also like to thank Erik Larrabee, with whom I have had countless discussions about my work.

Lastly, I would like to dedicate this work to my parents, Dilipkumar and Deepali Rane. Their belief, support, encouragement, and endless love has gotten me to where I am today, and for that, I will be forever grateful.
