\chapter{Adaptive Strategies}

In this section, we focus on adaptive LES of flow over a surging airfoil at different conditions. Problem setup, and baseline results including vortex detection and tracking, are first presented using the non-adapated mesh. We also present active flow control cases in the form of active reflex camber. Next, we present the three adaptive strategies and corresponding results. 

\input{chapters/adapt_strat/baseline_results}
\label{sec:baseline_results}

\section{Overview of Adaptive Strategies}

In this section, we focus on the low Reynolds number case of $Re=40,000$ at an angle of attack of $\alpha=6^\circ$ and advance ratio of $\mu_{sect}=1.2$. We explore three different adaptation strategies for mesh adaptation based on the VMS-based estimated error. 

The first strategy we employ is error estimator based zonal refinement/adaptation. 
In this strategy, we obtain an initial solution on a baseline mesh for the problem at hand. The VMS-based error estimator is then applied to the solution corresponding to this mesh, and based on the estimated error, the mesh is refined by a factor of 2 in particular zones where high error values are found. Estimated error for this adapted mesh is then calculated, and the mesh is again refined by a factor of 2 in zones of high error. This process is repeated till it is computationally feasible, or a convergence is reached.

The second strategy we employ is fully automated mesh adaptation based on the VMS-based error estimator. In this strategy, the estimated error and a specified target error are used to compute the desired mesh size or resolution in a local fashion, i.e., at every mesh vertex. We refer to this as the nodal size field, and the mesh is refined or coarsened based on this nodal size field. 

The third strategy is to employ feature-based refinement/adaptation. This allows for refinement around dominant flow features and also along the path/trajectory of such features, for example, the paths of leading and trailing edge vortices (LEV and TEV) over a surging cycle using vortex tracking. By running an initial simulation, we can get information on the approximate path that a certain feature will follow, estimate the error along this path, and perform refinement/adaptation along this path. 

Further details and applications of these three strategies are included in the following sections.

\subsection{Zonal Refinement/Adaptation}
\input{chapters/adapt_strat/zonal_based}

\subsection{Nodal Size Field-based Adaptation}
\input{chapters/adapt_strat/size_based}

\subsection{Feature-based Refinement/Adaptation}
\input{chapters/adapt_strat/feature_based}
\label{sec:feature_based_strat}


\subsection{Results using Different Adaptive Strategies}
\input{chapters/adapt_strat/Results}
\label{sec:results_adapt}
