\label{sec:VMS_NS}
As discussed previously, the Navier-Stokes equations possess advective and diffusive properties and extending the stabilization expressions from the 1D advection-diffusion to 3D Navier-Stokes have been effective in previous works.
We follow the same path for applying Equation \ref{eq:VMSerr} to each momentum component of the Navier-Stokes equations and arrive at the following

\begin{align}
    \seminorm{\bm{e}^{NS}}^2_{\HOne(\Omega^h)} &= \sum_{i}\seminorm{e^{NS}_i}^2_{\HOne(\Omega^h_k)} \\
    \seminorm{e^{NS}_i}_{\HOne(\Omega^h_k)} &= \seminorm{u_i'}_{\HOne(\Omega^h_k)} \approx \nu^{err,NS}_{k} \norm{\mathcal{R}^{NS}_i (\bar{u}_k)}_{L^2(\Omega^h_k)} \\
    \nu^{err,NS}_{k} &= \dfrac{1}{\sqrt{ \nu\sqrt{\bar{u}_i g_{ij} \bar{u}_j} + 3\nu^2\sqrt{g_{ij}g_{ij}}  }  } \\
    \label{eq:VMSerrNS}
\end{align} 

\noindent which uses the strong-form residual of the momentum equation due to the coarse-scale solution: $R^{NS}_i(\bar{u})=R^{NS}_i(u^h)$.

The discretization error resulting from the continuity equation is ignored since it is generally insignificant compared to the momentum discretization error.

\iffalse
One noticeable omission from the $\nu^{err}_e$ expression is any dependency on the time step, which is commonly found in stabilization expressions. 
As a reminder, the current form for the error-constant is derived from a steady-state advection-diffusion problem, and we are interested in the effectiveness of this current form.
Any extensions to the error-constant pave the way for future work.

This approach differs from previous work in that we use the $\HOne$-seminorm to measure the error whereas Hauke et al. \cite{hauke2008variational,hauke2015variational} focuses on the $L^2$ and $L^1$ norms. 
Moreover, we reach the form of the error constant through a direct extension of the 1D advection-diffusion setting to multidimensional settings which has not been done previously.
\fi

