\chapter{VMS based error estimator}

\label{chapter:APEE} %a posteriori error estimator

In this work, we focus on controlling the spatial discretization error through an \textit{a posteriori} error estimate.
Ideally, \textit{a posteriori} error estimate must provide pointwise the exact error, $e^{exact}=u-u^h$, where $u$ is the exact solution and $u^h$ is the numerical approximation $u$, since knowing how the error varies over space allows us to better choose our spatial discretization. 
Of course, knowledge of the exact error implies knowledge of the true solution rendering the simulation pointless.
Therefore, we employ an approximate error estimate $\apee$ measured in some norm of interest such as the $L^2$ norm, $\HOne$ norm, or $\HOne$ semi-norm.
We would like that the the error estimate has a local representation over an element $k$ and bounds (from above) the exact error.

%The local error estimate property provides a means of motivating adaptive methods and the upper-bound property provides safety against underestimating the global error. 
%An additional desired, but signficantly stronger, property would be to have the local error estimate bound the local true error.
%To measure the performance of an error estimate, it is common practice to look at the global effectivity index, $\eta$, or simply effectivity

%\begin{equation}
%%\eta = \frac{\apee}{||u-u^h||_{*}}
%\eta = \frac{\apee}{||e||_{*}^{exact}}
%\end{equation}

%\noindent which is the ratio between the estimated error and the exact error.
%Note that a local effectivity can also be defined on the element-level.

Many estimators, both explicit and implicit, have been developed and studied in the literature (e.g. see books by Ainsworth and Oden \cite{ainsworth2011book}, Verf\"urth \cite{verfurth2013posteriori}).
%and convection-diffusion systems (reviewed by John \cite{john2000numerical} and Verfurth \cite{verfurth2005robust}).
More recently, progress has been made in obtaining reliable explicit error estimates for the Navier-Stokes equations through the variational multi-scale approach (e.g. Hauke, Fuster, and Lizarraga \cite{hauke2015variational}).
%Although even in the context of convection-diffusion systems, John \cite{john2000numerical} finds that there is no optimal approach for all situations.
We employ the VMS-based error estimator since the VMS framework is currently used for LES and it is computationally inexpensive.

%In this work, we develop an explicit error estimator for the Navier-Stokes equations similar to that found in Hauke \textit{et al} \cite{hauke2015variational} in that we take advantage of the variational multiscale approach (VMS), which yield local error estimates in the norm of our choice. 
%A primary difference is in the norm which we choose to measure the error - $\HOne$ seminorm vs. $L^2$ or $L^1$.
We first review the general formulation of the VMS approach.
We then discuss the error estimator based on the VMS approach for a model 1D advection-diffusion problem followed by how it can be extended to a multi-dimensional setting.
We then extend the VMS-based error estimator to the Navier-Stokes equations and periodic problems of interest.

\section{General Formulation}
\label{sec:VMS_form}

%What is VMS?

The VMS paradigm relies on the idea of decomposing spaces of interest into coarse-scale and fine-scale subspaces.
The coarse-scale space represents our choice of spatial discretization and is therefore finite dimensional, whereas the fine-scale space encompasses the remainder of the space that our discretization cannot represent and is therefore infinite dimensional.
More importantly, the fine-scale space is necessarily a representation of the spatial discretization error for the solution space.

Let us specifically consider the trial and weighting spaces for some model finite element problem as $\mathcal{S}$ and $\mathcal{W}$, respectively.
Let $\bar{\mathcal{S}}$ be a subset of $\mathcal{S}$ and let $\Projector: \mathcal{S} \rightarrow \bar{\mathcal{S}}$ be a linear projector such that $\Projector u = \bar{u}$ where $u \in \mathcal{S}$, $\bar{u} \in \bar{\mathcal{S}}$, and $Range(\Projector)=\bar{\mathcal{S}}$.
This naturally leads to the definition of a complementary space $\mathcal{S}' = Kernel(\Projector)$ and allows for the direct sum decomposition $\mathcal{S} = \bar{\mathcal{S}} \oplus \mathcal{S}'$ and $\mathcal{W}$ = $\bar{\mathcal{W}} \oplus \mathcal{W}'$, where $\bar{\mathcal{S}}$ and $\bar{\mathcal{W}}$ represent the coarse-scale subspaces and $\mathcal{S}'$ and $\mathcal{W}'$ represent the fine-scale subspaces.
$\bar{\mathcal{S}}$ is the same as $\mathcal{S}^h$ and $\bar{u}$ is the same as $u^h$. This equivalence applies for the coarse-scale weighting space as well. 
We use the $\bar{\cdot}$ notation in this section to be consistent with the most prevalant literature on VMS-based error estimation (i.e., it is slightly different from the notation used in the previous section).

Because of the direct-sum representation, we can also state that $u=\bar{u}+u'$ is a unique decomposition where $\bar{u} \in \bar{\mathcal{S}}$ and $u' \in \mathcal{S}'$ for any $u \in \mathcal{S}$.

Consider the usual statement of a homogeneous linear partial-differential equation with linear operator $\mathcal{L}$ and forcing function $f$

\begin{equation}
    \mathcal{L}(u) = f \qquad u|_{\Gamma} = 0
    \label{eq:modelProblem}
\end{equation} 

\noindent which yields the following finite element problem:
find $u \in \mathcal{S}$ such that

\begin{equation}
    B(w,u) = (w,f), \qquad \forall w \in \mathcal{W}
\end{equation} 

\noindent where $B(\cdot,\cdot)$ is a bilinear form stemming from integration by parts of Equation \ref{eq:modelProblem} and $(\cdot,\cdot)$ is the $L^2$ inner product.

Applying the scale decomposition and leveraging the direct-sum representation yields a coarse-scale problem and a fine-scale problem.

Find $\bar{u} \in \bar{\mathcal{S}}$ such that
\begin{equation}
    B(\bar{w},\bar{u}) + B(\bar{w},u') = B(\bar{w},\bar{u}) + (\mathcal{L}^{*}\bar{w},u') = (\bar{w},f), \qquad \forall \bar{w} \in \bar{\mathcal{W}}
\end{equation} 

Find $u' \in \mathcal{S}'$ such that
\begin{equation}
    B(w',\bar{u}) + B(w',u') = (w',\mathcal{L}\bar{u}) + B(w',u') = (w',f), \qquad \forall w' \in \mathcal{W}'
    \label{eq:fineScale}
\end{equation}

The coarse-scale problem is coupled with the fine-scale problem through $u'$, which again is conveniently also a representation of the discretization error.
A further remark is that the coarse-scale problem has the form of a stabilized finite element method once a substitution for the form of $u'$ is made.
The fine-scale problem does afford a solution (see Hughes and Sangalli \cite{hughes2007variational}), where

\begin{equation}
    u'(y_i) = -\int_{\Omega} g'(x_i,y_i)(\mathcal{L}\bar{u}-f)(x_i) d\Omega
    \label{eq:uPrimeSoln}
\end{equation} 

\noindent where $g'(x_i,y_i)$ is the fine-scale Green's function with $x_i,y_j \in \Omega$, which is not known in general, except for certain cases - one of which is the 1D linear advection-diffusion equation.
Since the Navier-Stokes equations have advective and diffusive properties, we use the 1D linear advection-diffusion as a starting point to derive the a posteriori error estimator.

One final remark is that the form of the fine-scale Green's function is directly tied to the choice of projector $\Projector$.
This equivalently also means that the various choices of $\Projector$ leads to different unique pairings of $u$ and $u'$.
Hughes and Sangalli \cite{hughes2007variational} explored two options for the $\Projector$: $\Projector_{L^2}$ and $\Projector_{H^1}$, and found that for 1D advection-diffusion systems, the $\Projector_{H^1}$ led to a localization of $g'$ to single elements and led to an optimal solution for $\bar{u}$ in the $\HOne_0$-norm or $\HOne$-seminorm, making this choice a practical one.
The localization of $g'$ is ideal for constructing local error estimators.

\section{Formulation for 1D Advection-Diffusion Equation}
\input{chapters/VMS_EE/Formulation1D}
\label{sec:1D_AD}

\subsection{Application to the Navier-Stokes Equations}
\input{chapters/VMS_EE/App_toNS}

\subsection{Application to Periodic Problems}
\input{chapters/VMS_EE/App_toPeriodic}
\label{sec:app_to_periodic}

\subsection{Overview of Adaptive Strategies}
\input{chapters/VMS_EE/Adapt_St}
\label{sec:adapt_strat_overview}
%\section{Non-dimensionalization of Error}

%One convenient aspect of the VMS approach to obtaining an error estimate is that the resulting units of the estimate are  



%%%xxx LATER Add a multi-D case (internal layer or boundary layer). Add a comment on Ainsworth 2013 paper with global effectivity order 60-100 for Pe of O(100).

