\chapter{Adaptive LES of Flow Over Surging Airfoil}

In this chapter, we first investigate the three different mesh adaptation strategies based on the VMS-based estimated error to perform adaptive large eddy simulation of flow over a surging airfoil.
The zonal-based strategy is found to be most effective. This strategy is subsequently applied for adaptive LES, at two Reynolds numbers of $Re=40,000$ and $200,000$, to construct a series of adapted meshes for which mesh convergence is shown. In particular, for quantities of interest including pressure coefficient and leading edge vortex (LEV) evolution.
% A brief overview of the three strategies considered is mentioned in chapter \ref{sec:adapt_strat_overview}.

\section{Problem Setup}

The problem setup for these cases is the same as the one described in Section \ref{sec:problem_setup_baseline}.

\section{Summary of Cases}

In this chapter, NACA 0012 airfoil is considered at Reynolds number of $Re=40,000$ and $200,000$, and at a sectional advance ratio of $\mu_{sect}=1.2$ (i.e., higher value), see Table \ref{table:adapt_summary_cases}. Note that for the $Re=1,000,000$ case, the computational cost is significantly higher and it exhibits a similar flow behavior as the $Re=200,000$ case, especially in LEV evolution. Thus, $Re=40,000$ and $200,000$ are considered in this chapter for adaptive LES. Similarly, only higher advance ratio of $\mu_{sect}=1.2$ is considered for adaptive LES (since it shows more complex flow behaviour as compared to the lower advance ratio of $\mu_{sect}=1.0$).

\begin{table}[H]
	\centering
	\caption{Summary of surging cases for adaptive LES}
	\label{table:adapt_summary_cases}
	\begin{tabular}{|l|c|c|c|c|}
		\hline
		Airfoil   & $\alpha$ & $k$ & $\mu_{sect}$ & $Re$ \\
		\hline
		\hline
		NACA 0012 & 6$^\circ$ & $0.133$ &  1.2 & \{40,000,\; 200,000\} \\
		% \hline
		% NACA 0012 & 6$^\circ$ & $0.133$ & 1.2 & 200,000 \\
	\hline
	\end{tabular}
\end{table}

First, three different adaptive strategies are studied for the lower Reynolds number of $Re=40,000$, in which zonal-based strategy is found to be most effective. Subsequently, zonal-based strategy is used for both Reynolds numbers of $Re=40,000$ and $200,000$ to create a series of adapted meshes and show mesh convergence for adaptive LES.

% Next, adaptive LES is performed for $Re=40,000$ and $Re=200,000$ cases, where a series of adapted meshes is constructed, and mesh convergence is shown.

\section{Application and Comparison of Different Adaptive Strategies}
\label{sec:adaptive_strategy_comparison}
\input{chapters/adapt_strat/Adapt_St}



\section{Application of Zonal Refinement Strategy}


%In chapter \ref{sec:adaptive_strategy_comparison}, we established that the zonal based refinement is the most suitable strategy for accurate numerical solution of periodic problems in space and time using VMS-based error estimator driven mesh adaptation.
In this section, we focus on applying the zonal refinement. This is done for two cases with Reynolds numbers of $Re=40,000$ and $Re=200,000$, each at an angle of attack $\alpha=6^\circ$ and a sectional advance ratio of $\mu_{sect}=1.2$. As noted above, the computational cost is significantly higher for the $Re=1,000,000$ case and it exhibits a similar flow behavior as the $Re=200,000$ case, especially in LEV evolution. Thus, Reynolds numbers of $Re=40,000$ and $Re=200,000$ are considered for adaptive LES.

We explore mesh resolution effects in the in-plane and also in the spanwise direction. 
The run plan to achieve mesh convergence is as follows. 
We start off with an initial mesh that has a surface mesh resolution which meets the requirements for LES of wall-bounded boundary layer flows (when possible), or which is close to the required resolution. This mesh is referred to as M0.
On this initial mesh, we obtain the maximum error over multiple phases through the surging cycle and over the spanwise direction.
The in-plane mesh (corresponding to the airfoil section/plane) is then refined by a factor of 2 in regions of high error zones, i.e., we employ the zonal-based refinement strategy.
This resultant in-plane mesh after the first adaptation cycle is referred to as Mza1.
For this adaptation cycle, multiple spanwise resolutions are considered. Starting with the spanwise resolution of M0 mesh, a series of meshes for Mza1 with different spanwise resolutions are constructed.
In this series of meshes, spanwise resolution is refined by a factor of 2, till a convergence is achieved for this adaptation cycle. 
For the next adaptation cycle, zonal-based refinement is again employed to refine the in-plane mesh, and the mesh with the second highest spanwise resolution of the previous/first adaptation cycle is used as the initial spanwise resolution for the current/second adaptation cycle.
This mesh is referred to as Mza2.
Again, multiple spanwise resolutions are considered for this adaptation cycle.
This process is repeated for further adaptation cycles till mesh convergence is achieved (i.e., for both in-plane and spanwise refinements).

\subsection{ $Re=40,000$}


% M0\_nz25: 75 (strm) and 40 (span)
% Mza1\_nz25: 50 (strm) and 40 (span)
% Mza1\_nz50: 50 (strm) and 25 (span)
% Mza2\_nz50: 25 (strm) and 25 (span)
% Mza2\_nz100: 25 (strm) and 15 (span)
% Mza3\_nz50: 12 (strm) and 22 (span)
% Mza3\_nz100: 12 (strm) and 12 (span)


In this section, we focus on applying the zonal-based refinement strategy to the lower Reynolds number case of $Re=40,000$ at an angle of attack $\alpha=6^\circ$ and an advance ratio of $\mu_{sect}=1.2$.
As mentioned above, we start with an initial mesh that satisfies the surface mesh resolution criteria (for LES) in wall units at the maximum instantaneous Reynolds number over the surging cycle, which is achieved at $\psi=90^\circ$ (since relative velocity is the maximum at this phase). 
This mesh is referred to as M0\_nz25, where nz25 refers to the number of extruded layers in the spanwise direction (i.e., 25).

Next, Mza1 series of meshes is obtained using zonal-based refinement along with multiple spanwise resolutions. This series consists of three meshes: Mza1\_nz25, Mza1\_nz50 and Mza1\_nz100.
We observe that Mza1\_nz25 results compare well with those from Mza1\_nz50 and Mza1\_nz100, and thus, Mza1\_nz100 is omitted below for brevity and clarity.

For the next adaptation cycle, Mza2 series of meshes is obtained by applying  zonal-based refinement to the Mza1 mesh.
This series also consists of three meshes: Mza2\_nz25, Mza2\_nz50 and Mza2\_nz100. 
We observe that results from Mza2\_nz25 does not agree well with those from Mza2\_nz50 and Mza2\_nz100, whereas we observe a good agreement between Mza2\_nz50 and Mza2\_nz100.
Thus, Mza2\_nz25 is omitted for brevity.

For the next adaptation cycle, Mza3 series of meshes is obtained by applying  zonal-based refinement to the Mza2 mesh. 
This series consists of two meshes: Mza3\_nz50 and Mza3\_nz100.. 
We would like to note that the Mza3\_nz200 mesh is computationally very expensive for LES and is not considered.
Results from Mza3\_nz50 and Mza3\_nz100 agree well and are presented below.

In summary, results from 7 meshes (including the initial/M0 mesh) are presented for this case.

\pagebreak
\subsubsection{Adapted Meshes}
\input{chapters/zonal_adapt_results/mesh_and_error_field}
\label{sec:zonal_mesh_and_error}

\subsubsection{Force Response}
\input{chapters/zonal_adapt_results/force_response}
\label{sec:zonal_force_response}

\subsubsection{Flowfield: Spanwise Vorticity}
\input{chapters/zonal_adapt_results/vorticity}
\label{sec:zonal_vorticity}

\subsubsection{Pressure Coefficient}
\input{chapters/zonal_adapt_results/Cp}
\label{sec:zonal_cp}

\subsubsection{LEV Evolution}
\input{chapters/zonal_adapt_results/LEV}
\label{sec:zonal_LEV}


\subsection{ $Re=200,000$}

In this section, we focus on applying the zonal-based refinement strategy to the Reynolds number case of $Re=200,000$ at an angle of attack $\alpha=6^\circ$ and an advance ratio of $\mu_{sect}=1.2$.
As mentioned above, we start with an initial mesh that has a surface mesh resolution which is close to that required for LES of wall-bounded boundary layer flows. This is done at the maximum instantaneous Reynolds number over the surging cycle, which is achieved at $\psi=90^\circ$ (since relative velocity is the maximum at this phase). 
This mesh is referred to as M0\_nz50, where nz50 refers to the number of extruded layers in the spanwise direction (i.e., 50).
Next, Mza1\_nz50 is obtained using zonal-based refinement on M0\_nz50. And similarly Mza2\_nz50 is obtained using zonal-based refinement on Mza1\_nz50. In summary, 3 meshes (including the initial/M0 mesh) are considered for this case. More meshes will be considered in the future, e.g., Mza1\_nz100, Mza2\_100 and Mza3\_nz100.

\subsubsection{Adapted Meshes}
\input{chapters/zonal_adapt_results/mesh_and_error_field_Re200k}
\label{sec:zonal_mesh_and_error_Re200k}


\subsubsection{Force Response}
\input{chapters/zonal_adapt_results/force_response_Re200k}
\label{sec:zonal_force_response_Re200k}

\subsubsection{Flowfield: Spanwise Vorticity}
\input{chapters/zonal_adapt_results/vorticity_Re200k}
\label{sec:zonal_vorticity_Re200k}

\subsubsection{Pressure Coefficient}
\input{chapters/zonal_adapt_results/Cp_Re200k}
\label{sec:zonal_cp_Re200k}

\subsubsection{LEV Evolution}
\input{chapters/zonal_adapt_results/LEV_Re200k}
\label{sec:zonal_LEV_Re200k}



%\section{ $Re=40,000$,  $\alpha=10^\circ$, $\mu_{sect}=1.5$: Active Camber Case}

%\input{chapters/zonal_adapt_results/active_camber_adapt}
%\label{sec:zonal_active_camber}

